Constructing the transition graphs of interacting hysterons

### 2022-06-14 Paper_draft.tex
Added remaining references

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

Frustrated media can have rugged energy landscapes, with many metastable states. Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving. For a variety of systems, including sheared amorphous solids\cite{lindeman2021}( Keim \& Paulsen, 2019), crumpled thin sheets (Lahini, 2021), corrugated sheets\cite{bense2021} and origami structures (Lechenault, 2021) remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model(Nagel, 2021; Keim \& Paulsen, 2019) have been observed.\\ 

@@

The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving (Regev, 2019). Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons. For as few as three interacting hysterons, over 15,000 distinct graphs are found\cite{vhecke2021}. Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\

@@

In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling. The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients (Van Hecke, 2021).\\

@@

We can distinguish between two groups of base graphs. First, there are the Preisach graphs, which are possible without coupling. Second, there is a group of scrambled graphs, which are possible for interacting hysterons. Scrambling is a phenomenon previously seen in interacting hysterons (Van Hecke, 2021; Bense, 2021), where the order in which hysterons flip is not the same throughout the graph. It occurs when the ordering between the switching fields of two hysterons in the same phase are changed by one or more hysterons, and is therefore only possible for three or more hysterons. Remarkably, having introduced the concept of base graphs, we can identify scrambling as a feature of the base graph. We can thus separate the two coupling effects of scrambling and avalanches.\\

@@

\bibliography{test}% Produces the bibliography via BibTeX.

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

Frustrated media can have rugged energy landscapes, with many metastable states. Recent work has shown that the many metastable states in frustrated systems can lead to unusual pathways when the system is subject to driving. For a variety of systems, including sheared amorphous solids\cite{lindeman2021}\cite{keimpaulsen2021}, crumpled thin sheets\cite{shohat2021}, corrugated sheets\cite{bense2021} and origami structures\cite{juleslechenault2021} remarkable phenomena such as breaking of return-point memory, a multiperiodic response to cyclical driving, and transient memory as described by the park bench model \cite{lindeman2021}\cite{keimpaulsen2019} have been observed.\\ 

@@

The possible metastable states and transitions between these states for a given hysteron system can be portrayed as a directed graph, which captures all possible responses of the system to driving\cite{regev2019}. Numerical sampling work from our group has shown that the number of possible transition graphs for a system of interacting hysterons increases dramatically with the number of hysterons. For as few as three interacting hysterons, over 15,000 distinct graphs are found\cite{vhecke2021}. Because the number of possible transition graphs quickly grows overwhelming, a systematic method will be needed for categorizing the graphs.\\

@@

In recent work, the transition graphs for two- and three-hysteron systems were found using numerical sampling. The obtained graphs contain several noteworthy phenomena that are not possible in the Preisach model, such as breaking of loop return point memory, scrambling, multiperiodic cycles and long transients\cite{vhecke2021}.\\

@@

We can distinguish between two groups of base graphs. First, there are the Preisach graphs, which are possible without coupling. Second, there is a group of scrambled graphs, which are possible for interacting hysterons. Scrambling is a phenomenon previously seen in interacting hysterons\cite{vhecke2021}\cite{bense2021}, where the order in which hysterons flip is not the same throughout the graph. It occurs when the ordering between the switching fields of two hysterons in the same phase are changed by one or more hysterons, and is therefore only possible for three or more hysterons. Remarkably, having introduced the concept of base graphs, we can identify scrambling as a feature of the base graph. We can thus separate the two coupling effects of scrambling and avalanches.\\

@@

\bibliography{mybibliography}% Produces the bibliography via BibTeX.
\bibliographystyle{apsrev}
